---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Stijn Servaes"
date: "18/10/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diamond Price Prediction Application

- The Diamond Price Predicition Application Diamond is a product developed using **Shiny** within **RStudio**.

- Using the PageUp and PageDown keys, or the arrow keys, all the slides can be traversed.

## Data Used
The data used for this application is the diamonds data set, which is part of the ggplot2 package. This dataset contains information about 53940 diamonds with 10 variables.

```{r, echo=TRUE}
library("ggplot2")
head(diamonds)
```

## Application Overview

- The price of diamonds can be analysed using several parameters.
- The most common parameters are carat, cut, color and clarity.
- Set these parameters in the application in order to estimate the price of the diamond.

## Application Resources

Click the following link to use the application:
https://sservaes.shinyapps.io/pred_diam/

Click the link below for the compiled project files on GitHub:
https://github.com/sservaes/Coursera-Developing-Data-Products